### 2024-05-01 assets/chapter_3/channel_amplitude.tex
:triangular_flag_on_post: Viva

% This file was created by matlab2tikz.
%
%The latest updates can be retrieved from
%  http://www.mathworks.com/matlabcentral/fileexchange/22022-matlab2tikz-matlab2tikz
%where you can also make suggestions and rate matlab2tikz.
%
\definecolor{mycolor1}{rgb}{0.00000,0.44700,0.74100}%
\definecolor{mycolor2}{rgb}{0.85000,0.32500,0.09800}%
\definecolor{mycolor3}{rgb}{0.92900,0.69400,0.12500}%
%
\begin{tikzpicture}

\begin{axis}[%
width=4.036in,
height=0.407in,
at={(0.677in,3.198in)},
scale only axis,
bar shift auto,
xmin=0,
xmax=2,
xtick={1},
ymin=0,
ymax=0.01,
ytick={   0, 0.01},
axis background/.style={fill=white},
xmajorgrids,
ymajorgrids,
legend style={at={(0.5,1.03)}, anchor=south, legend columns=3, legend cell align=left, align=left, draw=white!15!black},
title style={font=\large}, label style={font=\large}, ticklabel style={font=\large}, legend style={font=\large}, scaled y ticks=false, yticklabel=\pgfkeys{/pgf/number format/.cd,fixed,precision=2}\pgfmathprintnumber{\tick}
]
\addplot[ybar, bar width=0.178, fill=mycolor1, draw=black, area legend] table[row sep=crcr] {%
1	0.00540099400856952\\
};
\addplot[forget plot, color=white!15!black] table[row sep=crcr] {%
0	0\\
2	0\\
};
\addlegendentry{No RIS}

@@

\begin{axis}[%
width=4.036in,
height=0.407in,
at={(0.677in,2.513in)},
scale only axis,
bar shift auto,
xmin=0,
xmax=3,
xtick={1, 2},
ymin=0,
ymax=0.01,
ytick={   0, 0.01},
axis background/.style={fill=white},
xmajorgrids,
ymajorgrids,
title style={font=\large}, label style={font=\large}, ticklabel style={font=\large}, legend style={font=\large}, scaled y ticks=false, yticklabel=\pgfkeys{/pgf/number format/.cd,fixed,precision=2}\pgfmathprintnumber{\tick}
]
\addplot[ybar, bar width=0.178, fill=mycolor1, draw=black, area legend] table[row sep=crcr] {%
1	0.00314170999160457\\
2	0.00572485908105548\\
};
\addplot[forget plot, color=white!15!black] table[row sep=crcr] {%
0	0\\
3	0\\
};
\addplot[ybar, bar width=0.178, fill=mycolor2, draw=black, area legend] table[row sep=crcr] {%
1	0.00502314747430184\\
2	0.00698106265038798\\
};
\addplot[forget plot, color=white!15!black] table[row sep=crcr] {%
0	0\\
3	0\\
};
\addplot[ybar, bar width=0.178, fill=mycolor3, draw=black, area legend] table[row sep=crcr] {%
1	0.00330170889121358\\
2	0.00768466635770749\\
};
\addplot[forget plot, color=white!15!black] table[row sep=crcr] {%
0	0\\
3	0\\
};
\end{axis}

\begin{axis}[%
width=4.036in,
height=0.407in,
at={(0.677in,1.828in)},
scale only axis,
bar shift auto,
xmin=0,
xmax=5,
xtick={1, 2, 3, 4},
ymin=0,
ymax=0.01,
ytick={   0, 0.01},
ylabel style={font=\color{white!15!black}},
ylabel={Channel amplitude},
axis background/.style={fill=white},
xmajorgrids,
ymajorgrids,
title style={font=\large}, label style={font=\large}, ticklabel style={font=\large}, legend style={font=\large}, scaled y ticks=false, yticklabel=\pgfkeys{/pgf/number format/.cd,fixed,precision=2}\pgfmathprintnumber{\tick}
]
\addplot[ybar, bar width=0.178, fill=mycolor1, draw=black, area legend] table[row sep=crcr] {%
1	0.0016696476908254\\
2	0.00438348129943761\\
3	0.00457133324563245\\
4	0.00586320993785494\\
};
\addplot[forget plot, color=white!15!black] table[row sep=crcr] {%
0	0\\
5	0\\
};
\addplot[ybar, bar width=0.178, fill=mycolor2, draw=black, area legend] table[row sep=crcr] {%
1	0.00326549483873511\\
2	0.00557307586676685\\
3	0.00614450761039544\\
4	0.00726164815517615\\
};
\addplot[forget plot, color=white!15!black] table[row sep=crcr] {%
0	0\\
5	0\\
};
\addplot[ybar, bar width=0.178, fill=mycolor3, draw=black, area legend] table[row sep=crcr] {%
1	0.00166671759288851\\
2	0.0056728199729895\\
3	0.00568370327308551\\
4	0.00789867646413342\\
};
\addplot[forget plot, color=white!15!black] table[row sep=crcr] {%
0	0\\
5	0\\
};
\end{axis}

\begin{axis}[%
width=4.036in,
height=0.407in,
at={(0.677in,1.143in)},
scale only axis,
bar shift auto,
xmin=0,
xmax=9,
xtick={1, 2, 3, 4, 5, 6, 7, 8},
ymin=0,
ymax=0.01,
ytick={   0, 0.01},
axis background/.style={fill=white},
xmajorgrids,
ymajorgrids,
title style={font=\large}, label style={font=\large}, ticklabel style={font=\large}, legend style={font=\large}, scaled y ticks=false, yticklabel=\pgfkeys{/pgf/number format/.cd,fixed,precision=2}\pgfmathprintnumber{\tick}
]
\addplot[ybar, bar width=0.178, fill=mycolor1, draw=black, area legend] table[row sep=crcr] {%
1	0.00121164184157658\\
2	0.00238340383353008\\
3	0.00380683420957256\\
4	0.00397337725168322\\
5	0.00492524818026471\\
6	0.00528740868681232\\
7	0.00572071220385092\\
8	0.00587459497346489\\
};
\addplot[forget plot, color=white!15!black] table[row sep=crcr] {%
0	0\\
9	0\\
};
\addplot[ybar, bar width=0.178, fill=mycolor2, draw=black, area legend] table[row sep=crcr] {%
1	0.00264154779713112\\
2	0.00407667250014311\\
3	0.0049500895867949\\
4	0.00561010487339341\\
5	0.00637593781159189\\
6	0.0066081911104957\\
7	0.00719542472167268\\
8	0.00721447474714219\\
};
\addplot[forget plot, color=white!15!black] table[row sep=crcr] {%
0	0\\
9	0\\
};
\addplot[ybar, bar width=0.178, fill=mycolor3, draw=black, area legend] table[row sep=crcr] {%
1	0.00139675837927404\\
2	0.00297327122282322\\
3	0.00519768343232529\\
4	0.00524568965358895\\
5	0.00679027772006842\\
6	0.00680292145999757\\
7	0.00768611044981794\\
8	0.00771790378640739\\
};
\addplot[forget plot, color=white!15!black] table[row sep=crcr] {%
0	0\\
9	0\\
};
\end{axis}

\begin{axis}[%
width=4.036in,
height=0.407in,
at={(0.677in,0.458in)},
scale only axis,
bar shift auto,
xmin=0,
xmax=17,
xtick={ 1,  2,  3,  4,  5,  6,  7,  8,  9, 10, 11, 12, 13, 14, 15, 16},
xlabel style={font=\color{white!15!black}},
xlabel={Sorted subband index},
ymin=0,
ymax=0.01,
ytick={   0, 0.01},
axis background/.style={fill=white},
xmajorgrids,
ymajorgrids,
title style={font=\large}, label style={font=\large}, ticklabel style={font=\large}, legend style={font=\large}, scaled y ticks=false, yticklabel=\pgfkeys{/pgf/number format/.cd,fixed,precision=2}\pgfmathprintnumber{\tick}
]
\addplot[ybar, bar width=0.178, fill=mycolor1, draw=black, area legend] table[row sep=crcr] {%
1	0.0011086419762005\\
2	0.00139817672195447\\
3	0.00200749223129634\\
4	0.00276896018192483\\
5	0.00348858569071252\\
6	0.00390863609607119\\
7	0.00410205684728188\\
8	0.00421746375099375\\
9	0.0046579451399174\\
10	0.00494987881895202\\
11	0.00517723522936086\\
12	0.00554845359626313\\
13	0.00558432983698075\\
14	0.00581133838542614\\
15	0.00582728083668895\\
16	0.00588378650142745\\
};
\addplot[forget plot, color=white!15!black] table[row sep=crcr] {%
0	0\\
17	0\\
};
\addplot[ybar, bar width=0.178, fill=mycolor2, draw=black, area legend] table[row sep=crcr] {%
1	0.00243240737767257\\
2	0.00291012490661641\\
3	0.00364483122694576\\
4	0.00450699183712641\\
5	0.00487492494056207\\
6	0.00519805292278296\\
7	0.00528263562038442\\
8	0.00589785004825321\\
9	0.0059831692545346\\
10	0.00639251285950617\\
11	0.00669911334288142\\
12	0.00680111371923813\\
13	0.00709923174422509\\
14	0.0071115147925566\\
15	0.00725582025143191\\
16	0.00726750007562416\\
};
\addplot[forget plot, color=white!15!black] table[row sep=crcr] {%
0	0\\
17	0\\
};
\addplot[ybar, bar width=0.178, fill=mycolor3, draw=black, area legend] table[row sep=crcr] {%
1	0.00123628236378877\\
2	0.00164057003125897\\
3	0.00244260991306404\\
4	0.00355854925167237\\
5	0.00469336613331463\\
6	0.00513906379517623\\
7	0.00552284927791181\\
8	0.00566659546513512\\
9	0.00636655282038687\\
10	0.0064643206674846\\
11	0.00710638804550398\\
12	0.00714275219594531\\
13	0.00755098826468563\\
14	0.00759919845334804\\
15	0.00776427719266845\\
16	0.00777739000911697\\
};
\addplot[forget plot, color=white!15!black] table[row sep=crcr] {%
0	0\\
17	0\\
};
\end{axis}
\end{tikzpicture}%

>>>>

% This file was created by matlab2tikz.
%
%The latest updates can be retrieved from
%  http://www.mathworks.com/matlabcentral/fileexchange/22022-matlab2tikz-matlab2tikz
%where you can also make suggestions and rate matlab2tikz.
%
\definecolor{mycolor1}{rgb}{0.00000,0.44700,0.74100}%
\definecolor{mycolor2}{rgb}{0.85000,0.32500,0.09800}%
\definecolor{mycolor3}{rgb}{0.92900,0.69400,0.12500}%
%
\begin{tikzpicture}[font=\footnotesize]

\begin{axis}[%
width=4.036in,
height=0.407in,
at={(0.677in,3.198in)},
scale only axis,
bar shift auto,
xmin=0,
xmax=2,
xtick={1},
ymin=0,
ymax=0.01,
ytick={   0, 0.01},
axis background/.style={fill=white},
xmajorgrids,
ymajorgrids,
legend style={at={(0.5,1.03)}, anchor=south, legend columns=3, legend cell align=left, align=left, draw=white!15!black},
scaled y ticks=false, yticklabel=\pgfkeys{/pgf/number format/.cd,fixed,precision=2}\pgfmathprintnumber{\tick}
]
\addplot[ybar, bar width=0.178, fill=mycolor1, draw=black, area legend] table[row sep=crcr] {%
1	0.00540099400856952\\
};
\addplot[forget plot, color=white!15!black] table[row sep=crcr] {%
0	0\\
2	0\\
};
\addlegendentry{No RIS}

@@

\begin{axis}[%
width=4.036in,
height=0.407in,
at={(0.677in,2.513in)},
scale only axis,
bar shift auto,
xmin=0,
xmax=3,
xtick={1, 2},
ymin=0,
ymax=0.01,
ytick={   0, 0.01},
axis background/.style={fill=white},
xmajorgrids,
ymajorgrids,
scaled y ticks=false, yticklabel=\pgfkeys{/pgf/number format/.cd,fixed,precision=2}\pgfmathprintnumber{\tick}
]
\addplot[ybar, bar width=0.178, fill=mycolor1, draw=black, area legend] table[row sep=crcr] {%
1	0.00314170999160457\\
2	0.00572485908105548\\
};
\addplot[forget plot, color=white!15!black] table[row sep=crcr] {%
0	0\\
3	0\\
};
\addplot[ybar, bar width=0.178, fill=mycolor2, draw=black, area legend] table[row sep=crcr] {%
1	0.00502314747430184\\
2	0.00698106265038798\\
};
\addplot[forget plot, color=white!15!black] table[row sep=crcr] {%
0	0\\
3	0\\
};
\addplot[ybar, bar width=0.178, fill=mycolor3, draw=black, area legend] table[row sep=crcr] {%
1	0.00330170889121358\\
2	0.00768466635770749\\
};
\addplot[forget plot, color=white!15!black] table[row sep=crcr] {%
0	0\\
3	0\\
};
\end{axis}

\begin{axis}[%
width=4.036in,
height=0.407in,
at={(0.677in,1.828in)},
scale only axis,
bar shift auto,
xmin=0,
xmax=5,
xtick={1, 2, 3, 4},
ymin=0,
ymax=0.01,
ytick={   0, 0.01},
ylabel style={font=\color{white!15!black}},
ylabel={Channel amplitude},
axis background/.style={fill=white},
xmajorgrids,
ymajorgrids,
scaled y ticks=false, yticklabel=\pgfkeys{/pgf/number format/.cd,fixed,precision=2}\pgfmathprintnumber{\tick}
]
\addplot[ybar, bar width=0.178, fill=mycolor1, draw=black, area legend] table[row sep=crcr] {%
1	0.0016696476908254\\
2	0.00438348129943761\\
3	0.00457133324563245\\
4	0.00586320993785494\\
};
\addplot[forget plot, color=white!15!black] table[row sep=crcr] {%
0	0\\
5	0\\
};
\addplot[ybar, bar width=0.178, fill=mycolor2, draw=black, area legend] table[row sep=crcr] {%
1	0.00326549483873511\\
2	0.00557307586676685\\
3	0.00614450761039544\\
4	0.00726164815517615\\
};
\addplot[forget plot, color=white!15!black] table[row sep=crcr] {%
0	0\\
5	0\\
};
\addplot[ybar, bar width=0.178, fill=mycolor3, draw=black, area legend] table[row sep=crcr] {%
1	0.00166671759288851\\
2	0.0056728199729895\\
3	0.00568370327308551\\
4	0.00789867646413342\\
};
\addplot[forget plot, color=white!15!black] table[row sep=crcr] {%
0	0\\
5	0\\
};
\end{axis}

\begin{axis}[%
width=4.036in,
height=0.407in,
at={(0.677in,1.143in)},
scale only axis,
bar shift auto,
xmin=0,
xmax=9,
xtick={1, 2, 3, 4, 5, 6, 7, 8},
ymin=0,
ymax=0.01,
ytick={   0, 0.01},
axis background/.style={fill=white},
xmajorgrids,
ymajorgrids,
scaled y ticks=false, yticklabel=\pgfkeys{/pgf/number format/.cd,fixed,precision=2}\pgfmathprintnumber{\tick}
]
\addplot[ybar, bar width=0.178, fill=mycolor1, draw=black, area legend] table[row sep=crcr] {%
1	0.00121164184157658\\
2	0.00238340383353008\\
3	0.00380683420957256\\
4	0.00397337725168322\\
5	0.00492524818026471\\
6	0.00528740868681232\\
7	0.00572071220385092\\
8	0.00587459497346489\\
};
\addplot[forget plot, color=white!15!black] table[row sep=crcr] {%
0	0\\
9	0\\
};
\addplot[ybar, bar width=0.178, fill=mycolor2, draw=black, area legend] table[row sep=crcr] {%
1	0.00264154779713112\\
2	0.00407667250014311\\
3	0.0049500895867949\\
4	0.00561010487339341\\
5	0.00637593781159189\\
6	0.0066081911104957\\
7	0.00719542472167268\\
8	0.00721447474714219\\
};
\addplot[forget plot, color=white!15!black] table[row sep=crcr] {%
0	0\\
9	0\\
};
\addplot[ybar, bar width=0.178, fill=mycolor3, draw=black, area legend] table[row sep=crcr] {%
1	0.00139675837927404\\
2	0.00297327122282322\\
3	0.00519768343232529\\
4	0.00524568965358895\\
5	0.00679027772006842\\
6	0.00680292145999757\\
7	0.00768611044981794\\
8	0.00771790378640739\\
};
\addplot[forget plot, color=white!15!black] table[row sep=crcr] {%
0	0\\
9	0\\
};
\end{axis}

\begin{axis}[%
width=4.036in,
height=0.407in,
at={(0.677in,0.458in)},
scale only axis,
bar shift auto,
xmin=0,
xmax=17,
xtick={ 1,  2,  3,  4,  5,  6,  7,  8,  9, 10, 11, 12, 13, 14, 15, 16},
xlabel style={font=\color{white!15!black}},
xlabel={Sorted subband index},
ymin=0,
ymax=0.01,
ytick={   0, 0.01},
axis background/.style={fill=white},
xmajorgrids,
ymajorgrids,
scaled y ticks=false, yticklabel=\pgfkeys{/pgf/number format/.cd,fixed,precision=2}\pgfmathprintnumber{\tick}
]
\addplot[ybar, bar width=0.178, fill=mycolor1, draw=black, area legend] table[row sep=crcr] {%
1	0.0011086419762005\\
2	0.00139817672195447\\
3	0.00200749223129634\\
4	0.00276896018192483\\
5	0.00348858569071252\\
6	0.00390863609607119\\
7	0.00410205684728188\\
8	0.00421746375099375\\
9	0.0046579451399174\\
10	0.00494987881895202\\
11	0.00517723522936086\\
12	0.00554845359626313\\
13	0.00558432983698075\\
14	0.00581133838542614\\
15	0.00582728083668895\\
16	0.00588378650142745\\
};
\addplot[forget plot, color=white!15!black] table[row sep=crcr] {%
0	0\\
17	0\\
};
\addplot[ybar, bar width=0.178, fill=mycolor2, draw=black, area legend] table[row sep=crcr] {%
1	0.00243240737767257\\
2	0.00291012490661641\\
3	0.00364483122694576\\
4	0.00450699183712641\\
5	0.00487492494056207\\
6	0.00519805292278296\\
7	0.00528263562038442\\
8	0.00589785004825321\\
9	0.0059831692545346\\
10	0.00639251285950617\\
11	0.00669911334288142\\
12	0.00680111371923813\\
13	0.00709923174422509\\
14	0.0071115147925566\\
15	0.00725582025143191\\
16	0.00726750007562416\\
};
\addplot[forget plot, color=white!15!black] table[row sep=crcr] {%
0	0\\
17	0\\
};
\addplot[ybar, bar width=0.178, fill=mycolor3, draw=black, area legend] table[row sep=crcr] {%
1	0.00123628236378877\\
2	0.00164057003125897\\
3	0.00244260991306404\\
4	0.00355854925167237\\
5	0.00469336613331463\\
6	0.00513906379517623\\
7	0.00552284927791181\\
8	0.00566659546513512\\
9	0.00636655282038687\\
10	0.0064643206674846\\
11	0.00710638804550398\\
12	0.00714275219594531\\
13	0.00755098826468563\\
14	0.00759919845334804\\
15	0.00776427719266845\\
16	0.00777739000911697\\
};
\addplot[forget plot, color=white!15!black] table[row sep=crcr] {%
0	0\\
17	0\\
};
\end{axis}
\end{tikzpicture}%

### 2024-05-01 assets/chapter_4/region_comparison.tex
:triangular_flag_on_post: Viva

\begin{axis}[%
	width=4.079in,
	height=3.432in,
at={(0.673in,0.356in)},
scale only axis,
xmin=0,
xmax=6.5227548374066,
xlabel style={font=\color{white!15!black}},
xlabel={Primary Rate [bits/s/Hz]},
ymin=0,
ymax=2,
ylabel style={font=\color{white!15!black}},
ylabel={Backscatter Rate [bits/BB]},
axis background/.style={fill=white},
xmajorgrids,
ymajorgrids,
legend style={at={(0.03,0.97)}, anchor=north west, legend cell align=left, align=left, draw=white!15!black},
align=center,
title style={font=\huge},
label style={font=\huge},
ticklabel style={font=\LARGE},
legend style={font=\LARGE},
reverse legend,
every axis plot/.append style={line width=2pt}
]
\addplot [color=mycolor1, line width=2.0pt, mark=triangle, mark options={solid, rotate=180, mycolor1}]
  table[row sep=crcr]{%
6.33724402501803	1.39764296268229\\
0	1.39764296268229\\
0	0\\
6.52275483678685	0\\
6.52275483678685	2.37312052924553e-08\\
6.38739454470992	1.3235811846854\\
6.35422040211439	1.38916612409166\\
6.34857862205488	1.39386686170527\\
6.3445353675389	1.39608085009443\\
6.34291602910554	1.3966977322109\\
6.34149846039129	1.39711118534274\\
6.34024731759122	1.39737797077851\\
6.3391350240222	1.3975379071887\\
6.33862394227692	1.39758701988787\\
6.33813974610465	1.39761939115801\\
6.33795313341839	1.39762818964178\\
6.33777036860279	1.39763482338317\\
6.3375913342378	1.3976394187338\\
6.33741590881855	1.39764209463684\\
6.33724402501803	1.39764296268229\\
};
\addlegendentry{RIScatter}

>>>>

\begin{axis}[%
width=4.014in,
height=1.552in,
at={(0.673in,0.356in)},
scale only axis,
xmin=0,
xmax=6.5227548374066,
xlabel style={font=\color{white!15!black}},
xlabel={Primary Rate [bits/s/Hz]},
ymin=0,
ymax=2,
ylabel style={font=\color{white!15!black}},
ylabel={Backscatter\\Rate [bits/BB]},
axis background/.style={fill=white},
xmajorgrids,
ymajorgrids,
legend style={at={(0.03,0.97)}, anchor=north west, legend cell align=left, align=left, draw=white!15!black},
align=center,
% title style={font=\LARGE},
% label style={font=\LARGE},
% ticklabel style={font=\Large},
% legend style={font=\Large},
reverse legend,
every axis plot/.append style={line width=2pt}
]
\addplot [color=mycolor1, line width=2.0pt, mark=triangle, mark options={solid, rotate=180, mycolor1}]
  table[row sep=crcr]{%
6.33724402501803	1.39764296268229\\
0	1.39764296268229\\
0	0\\
6.52275483678685	0\\
6.52275483678685	2.37312052924553e-08\\
6.38739454470992	1.3235811846854\\
6.35422040211439	1.38916612409166\\
6.34857862205488	1.39386686170527\\
6.3445353675389	1.39608085009443\\
6.34291602910554	1.3966977322109\\
6.34149846039129	1.39711118534274\\
6.34024731759122	1.39737797077851\\
6.3391350240222	1.3975379071887\\
6.33862394227692	1.39758701988787\\
6.33813974610465	1.39761939115801\\
6.33795313341839	1.39762818964178\\
6.33777036860279	1.39763482338317\\
6.3375913342378	1.3976394187338\\
6.33741590881855	1.39764209463684\\
6.33724402501803	1.39764296268229\\
};
\addlegendentry{RIScatter}

### 2024-05-01 assets/viva/region_comparison.tex
:triangular_flag_on_post: Viva

\begin{axis}[%
	width=4.079in,
	height=3.432in,
at={(0.673in,0.356in)},
scale only axis,
xmin=0,
xmax=6.5227548374066,
xlabel style={font=\color{white!15!black}},
xlabel={Primary Rate [bits/s/Hz]},
ymin=0,
ymax=2,
ylabel style={font=\color{white!15!black}},
ylabel={Backscatter Rate [bits/BB]},
axis background/.style={fill=white},
xmajorgrids,
ymajorgrids,
legend style={at={(0.03,0.97)}, anchor=north west, legend cell align=left, align=left, draw=white!15!black},
align=center,
title style={font=\huge},
label style={font=\huge},
ticklabel style={font=\LARGE},
legend style={font=\LARGE},
reverse legend,
every axis plot/.append style={line width=2pt}
]
\addplot [color=mycolor1, line width=2.0pt, mark=triangle, mark options={solid, rotate=180, mycolor1}]
  table[row sep=crcr]{%
6.33724402501803	1.39764296268229\\
0	1.39764296268229\\
0	0\\
6.52275483678685	0\\
6.52275483678685	2.37312052924553e-08\\
6.38739454470992	1.3235811846854\\
6.35422040211439	1.38916612409166\\
6.34857862205488	1.39386686170527\\
6.3445353675389	1.39608085009443\\
6.34291602910554	1.3966977322109\\
6.34149846039129	1.39711118534274\\
6.34024731759122	1.39737797077851\\
6.3391350240222	1.3975379071887\\
6.33862394227692	1.39758701988787\\
6.33813974610465	1.39761939115801\\
6.33795313341839	1.39762818964178\\
6.33777036860279	1.39763482338317\\
6.3375913342378	1.3976394187338\\
6.33741590881855	1.39764209463684\\
6.33724402501803	1.39764296268229\\
};
\addlegendentry{RIScatter}

>>>>

\begin{axis}[%
	width=4.079in,
	height=3.432in,
at={(0.673in,0.356in)},
scale only axis,
xmin=0,
xmax=6.5227548374066,
xlabel style={font=\color{white!15!black}},
xlabel={Primary Rate [bits/s/Hz]},
ymin=0,
ymax=2,
ylabel style={font=\color{white!15!black}},
ylabel={Backscatter Rate [bits/BB]},
axis background/.style={fill=white},
xmajorgrids,
ymajorgrids,
legend style={at={(0.03,0.97)}, anchor=north west, legend cell align=left, align=left, draw=white!15!black},
align=center,
% title style={font=\huge},
% label style={font=\huge},
% ticklabel style={font=\LARGE},
% legend style={font=\LARGE},
reverse legend,
every axis plot/.append style={line width=2pt}
]
\addplot [color=mycolor1, line width=2.0pt, mark=triangle, mark options={solid, rotate=180, mycolor1}]
  table[row sep=crcr]{%
6.33724402501803	1.39764296268229\\
0	1.39764296268229\\
0	0\\
6.52275483678685	0\\
6.52275483678685	2.37312052924553e-08\\
6.38739454470992	1.3235811846854\\
6.35422040211439	1.38916612409166\\
6.34857862205488	1.39386686170527\\
6.3445353675389	1.39608085009443\\
6.34291602910554	1.3966977322109\\
6.34149846039129	1.39711118534274\\
6.34024731759122	1.39737797077851\\
6.3391350240222	1.3975379071887\\
6.33862394227692	1.39758701988787\\
6.33813974610465	1.39761939115801\\
6.33795313341839	1.39762818964178\\
6.33777036860279	1.39763482338317\\
6.3375913342378	1.3976394187338\\
6.33741590881855	1.39764209463684\\
6.33724402501803	1.39764296268229\\
};
\addlegendentry{RIScatter}

### 2024-05-01 content/abstract.tex
:pencil: Update chapter 3
:pencil: Add conclusion
:triangular_flag_on_post: Viva

% ************************** Thesis Abstract *****************************
% Use `abstract' as an option in the document class to print only the titlepage and the abstract.
\begin{abstract}
	\gls{ris} is the most promising physical-layer technology for 6G.
	It adopts many low-power scattering elements to customize the propagation environment for improved network performance, unlocking a new potential of \emph{channel design} as never before.
	In this dissertation, we first provide an overview of its structure, characteristics, applications, principles, and models, then discuss how it addresses the key issues in \gls{swipt} and compare it with \gls{bc} in terms of functionalities, principles, models, and preferences.
	The work chapters investigate three typical use cases of \gls{ris}: Joint design with transceiver for a particular objective (beamforming); ride its own information over legacy networks (modulation); and manipulate the wireless environment as a stand-alone device (channel shaping).
	In particular,
	\begin{itemize}
		\item \emph{\gls{ris}-aided \gls{swipt}:} We introduce \gls{ris} into multi-antenna, multi-carrier \gls{swipt} systems, investigating joint waveform and beamforming design for maximizing harvested energy under various communication rate constraints. Algorithms, performance trade-offs, and asymptotic behaviors are analyzed.
		\item \emph{RIScatter:} This novel scatter protocol integrates \gls{ris} and \gls{bc} from an input distribution perspective. The reflection pattern is exploited simultaneously for primary-link beamforming and backscatter-link modulation. We propose a practical cooperative receiver, characterize the achievable rate region, and analyze the impact of system parameters.
		\item \emph{\gls{mimo} channel shaping:} We exploit an advanced \gls{bd}-\gls{ris} architecture for singular value redistribution and power maximization in \gls{pc}, and leakage interference minimization in \gls{ic}.
		Their implications on rate-optimal joint designs are also discussed.
		We highlight the unique features of \gls{bd}-\gls{ris} and propose an efficient design framework.
	\end{itemize}
\end{abstract}

>>>>

% ************************** Thesis Abstract *****************************
% Use `abstract' as an option in the document class to print only the titlepage and the abstract.
\begin{abstract}
	\gls{ris} is one of the most promising physical-layer technology for 6G.
	It adopts numerous low-power scattering elements to customize the propagation environment for improved network performance, unlocking a new potential of \emph{channel design} as never before.
	In this dissertation, we first provide an overview of its physical structure, characteristics, applications, and scattering models, then discuss how it addresses the key issues in \gls{swipt} and compare it with \gls{bc} in terms of functionalities and preferences.
	The work chapters investigate three typical use cases of \gls{ris}: Joint design with transceiver for a specific performance measure (beamforming); ride its own information over legacy networks (modulation); and manipulate the inherent properties of the wireless environment as a stand-alone device (channel shaping).
	In particular, we address the following topics:
	\begin{itemize}
		\item \emph{\gls{ris}-aided \gls{swipt}:} We introduce \gls{ris} into multi-antenna, multi-carrier \gls{swipt} systems, investigating joint waveform and beamforming design. \gls{r-e} region of practical receivers are characterized under non-linear harvester and frequency-flat \gls{ris} models.
		\item \emph{RIScatter:} This novel scatter protocol integrates \gls{ris} and \gls{bc} from an input distribution perspective. The reflection pattern is exploited simultaneously for beamforming of the primary link and modulation of the backscatter link. We propose a practical cooperative receiver and characterize the achievable rate region.
		\item \emph{\gls{mimo} channel shaping:} We exploit an advanced \gls{bd}-\gls{ris} architecture for singular value redistribution in \gls{pc} and leakage interference minimization in \gls{ic}.
		Their implications on joint \gls{ris}-transceiver designs are also discussed.
		We also propose an efficient and universal \gls{bd}-\gls{ris} design framework.
	\end{itemize}
\end{abstract}
